\documentclass[margin,line]{res}

\usepackage{enumitem}
\usepackage{fontawesome}
\usepackage{hyperref}
\usepackage{xcolor}
\hypersetup{
	colorlinks,
	linkcolor={red!50!black},
	citecolor={red!50!black},
	urlcolor={blue!50!black}
}



\setcounter{page}{1}

\oddsidemargin -.5in
\evensidemargin -.5in
\textwidth=6.0in
\itemsep=0in
\parsep=0in
% if using pdflatex:
%\setlength{\pdfpagewidth}{\paperwidth}
%\setlength{\pdfpageheight}{\paperheight} 

\newenvironment{list1}{
  \begin{list}{\ding{113}}{%
      \setlength{\itemsep}{0in}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{0in} \setlength{\partopsep}{0in} 
      \setlength{\leftmargin}{0.17in}}}{\end{list}}
\newenvironment{list2}{
  \begin{list}{$\bullet$}{%
      \setlength{\itemsep}{0in}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{0in} \setlength{\partopsep}{0in} 
      \setlength{\leftmargin}{0.2in}}}{\end{list}}

\usepackage{setspace}
\renewcommand{\baselinestretch}{1.0} 


\begin{document}

\name{\huge Sanghoon Park \vspace*{.1in}}

\begin{resume}
\section{\sc Contact Information}
\vspace{.05in}
\begin{tabular}{@{}p{2in}p{4in}}
\faBuildingO\:\#305 Gambrell Hall & {\faPhoneSquare}  +1 (803) 626-2252 \\  
817 Henderson Street & {\faEnvelope}  \href{sp23@email.sc.edu}{\ttfamily sp23@email.sc.edu} \\

Columbia, SC 29208 & {\faChain} \href{sanghoon-park.com}{\ttfamily sanghoon-park.com}\\       
& {\faGithub} \href{https://github.com/pherephobia}{\ttfamily github.com/pherephobia}\\     
%& {ORCID ID}: \href{https://orcid.org/0000-0001-5365-0013}{0000-0001-5365-0013}

\end{tabular}

\section{\sc Education}
{\bf University of South Carolina}, Columbia, SC, US

\vspace*{-4mm}
Ph.D. Student in Political Science, expected 2023\\
%\hspace*{-8mm} Dissertation: {\it My Dissertation title}\\ 
\hspace*{3mm} Concentration: {\it Comparative Politics, International Relations}
%\hspace*{-8mm} Advisors: Drs. Wilson C.  (Biology) \& James G. McDaniel (Mechanical Engineering)	
\vspace*{-1.5mm}

{\bf Hankuk University of Foreign Studies}, Seoul, ROK

\vspace*{-4mm}
M.A. in Political Science and International Relations, February 2017\\
\vspace*{-4mm}
\begin{itemize} \itemsep -1mm 
	\item[]  \hspace*{-6mm} Thesis: {\it Dictatorships and Redistribution: Empirical Analysis of Redistribution by Dictatorship Sub-regime Types}
	\item[]  \hspace*{-6mm} Advisor: Dr. Jaemook Lee (Political Science), and specially Daejin Yi (Political Science)
\end{itemize}
\vspace*{-3mm}
B.A. in Political Science and International Relations, February 2015\\
\vspace*{-4mm}
\begin{itemize} \itemsep -1mm
	\item[]  \hspace*{-6mm} Major: Political Science and International Relations
	\item[]  \hspace*{-6mm} Minor: International Economics and Law
\end{itemize}

\section{\sc Research Interests}
{\bf Comparative Politics} Authoritarian regimes, Democratization, Regime breakdown, Comparative institutions, Political economics of inequality and redistribution

\vspace{-.3cm}
{\bf International Relations} Democratic diffusion, Economic sanctions, Foreign aids

\section{\sc Peer-Reviewed Articles}

\begin{enumerate}[leftmargin=*]
\item[7.] \textbf{Park, Sanghoon}, Chaehoon Lee, and Ilgi Kim. 2020. ``\href{https://www.earticle.net/Journal/Issues/511/28448}{Infectious Disease Management and New Security Strategies: The Case of African Swine Fever in South Korea}." \textit{The Journal of Peace Studies} 21(2): 143-174.
\item[6.] \textbf{Park, Sanghoon}, and Jaeyoung Hur. 2020. ``\href{http://www.discourse201.org/html/sub05_01.asp}{Does North Korea Policies Reflect Public Opinion? The Public Awareness Survey Around the 4.27 Panmunjom Declaration}." \textit{Discourse 201} 23(2): 83-113.
\item[5.] Lee, Jaehoon, and \textbf{Sagnhoon Park}. 2020. ``\href{https://m.nec.go.kr/portal/cmm/fms/FileDown.do?atchFileId=5d0ffae936edc42f3b4e864801f86a0f4096c44da03fede418b94067e8f9d0ea&fileSn=1&bbsId=&searchYear=}{Climate and Electoral Participation: The Effect of Particulate Matter on Election in South Korea}'' \textit{The study of Election} 1(12): 77-98.  
\item[4.] \textbf{Park, Sanghoon}, Jaemook Lee, and Daejin Yi. 2017. \href{http://www.dbpia.co.kr/Journal/ArticleDetail/NODE07183479?TotalCount=1&Seq=1&q=%5B%EB%8F%85%EC%9E%AC%EA%B5%AD%EA%B0%80%EC%99%80%20%EC%9E%AC%EB%B6%84%EB%B0%B0%C2%A7coldb%C2%A72%C2%A751%C2%A73%5D&searchWord=%EC%A0%84%EC%B2%B4%3D%5E%24%EB%8F%85%EC%9E%AC%EA%B5%AD%EA%B0%80%EC%99%80%20%EC%9E%AC%EB%B6%84%EB%B0%B0%5E*&Multimedia=0&isIdentifyAuthor=0&Collection=0&SearchAll=%EB%8F%85%EC%9E%AC%EA%B5%AD%EA%B0%80%EC%99%80%20%EC%9E%AC%EB%B6%84%EB%B0%B0&isFullText=0&specificParam=0&SearchMethod=0&Sort=1&SortType=desc&Page=1&PageSize=20#}{``Dictatorships and Redistribution: Empirical Analysis of Redistribution by Dictatorships Sub-regime Type."} \textit{OUGHTOPIA} 32(1), 271-314.
\item[3.] Oh, Sujin, \textbf{Sanghoon Park}, and Jaemook Lee. 2017. \href{http://www.dbpia.co.kr/Journal/ArticleDetail/NODE07131578?TotalCount=1&Seq=1&q=%5B%EC%9D%B4%EC%9E%AC%EB%AC%B5%20%EC%98%A4%EC%88%98%EC%A7%84%20%EB%B0%95%EC%83%81%ED%9B%88%20%EA%B3%84%EA%B8%89%ED%88%AC%ED%91%9C%C2%A7coldb%C2%A72%C2%A751%C2%A73%5D&searchWord=%EC%A0%84%EC%B2%B4%3D%5E%24%EC%9D%B4%EC%9E%AC%EB%AC%B5%20%EC%98%A4%EC%88%98%EC%A7%84%20%EB%B0%95%EC%83%81%ED%9B%88%20%EA%B3%84%EA%B8%89%ED%88%AC%ED%91%9C%5E*&Multimedia=0&isIdentifyAuthor=0&Collection=0&SearchAll=%EC%9D%B4%EC%9E%AC%EB%AC%B5%20%EC%98%A4%EC%88%98%EC%A7%84%20%EB%B0%95%EC%83%81%ED%9B%88%20%EA%B3%84%EA%B8%89%ED%88%AC%ED%91%9C&isFullText=0&specificParam=0&SearchMethod=0&Sort=1&SortType=desc&Page=1&PageSize=20#}{``Class Betrayal Voting and Political Knowledge in the 20th Korean General Election." \textit{Korean Political Science Review} 51(1), 153-180.}
\item[2.] Park, Youngdeuk, \textbf{Sanghoon Park}. 2016. \href{http://kiss.kstudy.com/thesis/thesis-view.asp?key=3472800}{``Determinants of Voting Choice in Brexit Referendum: Skill Level and Job Competition in the Labor Market."} \textit{The Korean Journal of Area Studies} 34(3), 1-31.	
\item[1.] \textbf{Park, Sanghoon}. 2015. \href{http://search.koreanstudies.net/thesis/thesis-view.asp?key=3438155}{``Welfare Expenditure and Economic Growth: The Sub-types of Welfare Expenditure of OECD countries."} \textit{Global Political Research} 9(2), 81-107.	
\end{enumerate}
\newpage

\section{\sc Other Publications}
\begin{enumerate}[leftmargin=*]
	\item[1.] \textbf{Park, Sanghoon} and Jaeyoung Hur. 2021. "What do we know and do not know?: Attitudes toward North Korea and unification." In {\it Issues and Perspectives in Korean Peace Process.} Hankuk University of Foreign Studies Knowledge Contents \& Press.
\end{enumerate}


\section{\sc Honors, Awards, and Grants} 

\begin{itemize}[wide = 0pt] \itemsep 1.5mm
	\item[2018-2023] \textbf{University of South Carolina, Department of Political Science, SC, US}
	\begin{itemize} 
		\item[$\circ$] ACAF 4.00 Graduate Assistantships
	\end{itemize} 
	\item[2020] \textbf{Empirical Implications of Theoretical Models Institute}
	\begin{itemize}
		\item[$\circ$] \href{https://52.2.147.143/icpsrweb/content/sumprog/scholarships/winners-2020.html}{EITM Certification Scholarships: Both sessions at the ICPSR Summer Program} (\$4,000)
	\end{itemize} 
	\item[2020] \textbf{Department of Political Science, University of South Carolina, SC, US}
	\begin{itemize}
		\item[$\circ$] Outstanding Graduate Student Awards
	\end{itemize} 
	\item[2020] \textbf{Department of Political Science, University of South Carolina, SC, US}
	\begin{itemize}
		\item[$\circ$] The Second Annual Conference Funding Competition: Joint award (\$500)
	\end{itemize} 
	\item[2019] \textbf{The Institute for National Security Strategy (INSS), Seoul, ROK}
	\begin{itemize}\itemsep -1mm 
		\item[$\circ$] The 1st New Security Papers Contest: Second Prize (\$2,000)
		\item[$\circ$] Title: Infectious Disease Management and New Security Strategies: The Case of African Swine Fever in South Korea
	\end{itemize}
	\item[2015-2017] \textbf{Hankuk University of Foreign Studies, Seoul, ROK}
	\begin{itemize} 
		\item[$\circ$] Merit based, Graduate Full Scholarship for HUFSAN
	\end{itemize}
\end{itemize}

\section{\sc Conference Presentations}

{\bf Park, Sanghoon}. {2020.} {``Why Do Authoritarian Regimes Provide Welfare Programs?''} {\it The Annual Conference for Midwest Political Science Association,} Chicago, IL, US.

\vspace{-.25cm}
{\bf Park, Sanghoon}. {2020.} \href{https://www.dropbox.com/s/7xr90ielm1vh1sd/poster.pdf?dl=0}{\tt Poster PDF.} {``When Does Water Bring Conflicts?''} {\it Carolinas Conflict Consortium,} Charlotte, NC, US.

\vspace{-.25cm}
{\bf Park, Sanghoon}. {2020.} {``Why Do Authoritarian Regimes Provide Welfare?''} {\it The Annual Conference for Southern Political Science Association,} San Juan, PR, US.

\vspace{-.25cm}
{\bf Park, Sanghoon}. {2019.} {``Why Do Authoritarian Regimes Provide Welfare?''} {\it The World Congress for Korean Politics and Society,} Seoul, ROK.

\section{\sc Extra Curriculum \& Skills} 


{\bf ICPSR Summer Program}, University of Michigan, MI, US, 2020.

\begin{itemize} \itemsep -1mm 
	\item[$\circ$] \textit{First Session: June 22-July 17, 2020}
	\begin{enumerate} \itemsep -1mm 
		\item Bayesian Modeling for the Social Sciences I: Introduction and Application
		\item Maximum Likelihood Estimation I: Generalized Linear Models
		\item Introduction to Python (July 6-17)
	\end{enumerate}
	\item[$\circ$] \textit{Second Session, July 20-August 14, 2020}
	\begin{enumerate} \itemsep -1mm 
		\item Game Theory
		\item Bayesian Modeling for the Social Sciences II: Advanced Topics
		\item Causal Inference for the Social Sciences
	\end{enumerate}
\end{itemize}


\mbox{}
\vfill
\centering \textit{Last updated: \today}


\end{resume}

\end{document}