\documentclass[11pt]{res} % default is 10 pt
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font 
\setlength{\textheight}{9.5in} % increase text height to fit resume on 1 page
\newcommand\tab[1][1cm]{\hspace*{#1}}
\usepackage[utf8]{inputenc}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{xcolor}
\hypersetup{
	colorlinks,
	linkcolor={red!50!black},
	citecolor={red!50!black},
	urlcolor={blue!50!black}
}
\usepackage{soul}
\usepackage[sc]{mathpazo}
\renewcommand{\labelitemiv}{$\circ$}
\pagestyle{plain}
\setcounter{page}{1}
\pagenumbering{arabic}
\linespread{1.05}         % Palladio needs more leading (space between lines)

\newsectionwidth{0pt}  % So the text is not indented under section headings

\begin{document} 

\name{\huge \bf Sang-hoon Park\\[12pt]} % the \\[12pt] adds a blank line after name
\address{University of South Carolina \\ 
	\#305 Gambrell Hall \\ 817 Henderson Street \\ Columbia, SC 29208}
\address{Email: sp23@email.sc.edu \\
	\href{https://shpark.netlify.com/}{https://shpark.netlify.com/} \\ Mobile (personal): (803) 626-2252 \\ \textit{ORCID ID}: \href{https://orcid.org/0000-0001-5365-0013}{0000-0001-5365-0013}}
 
                                             
\begin{resume}
                               
\section{EDUCATION} 
\noindent {\bf Ph.D. Student, \href{https://www.sc.edu/study/colleges_schools/artsandsciences/political_science/index.php}{University of South Carolina}} \\
 Department of Political Science, August 2018 - \textit{Present}
\begin{itemize}
 	\item[]  \hspace*{-8mm} \underline{\smash{Concentration: Comparative Politics, International Relations}}
\end{itemize}
\noindent {\bf M.A., \href{http://hufspol.hufs.ac.kr/}{Hankuk University of Foreign Studies}} \\
Department of Political Science and International Relations, February 2017
\begin{itemize} \itemsep -2pt 
	\item[] \hspace*{-8mm} \textit{Thesis:} ``Dictatorships and Redistribution: Empirical Analysis of Redistribution by Dictatorship Sub-regime Types."
	\item[] \hspace*{-5mm} \textit{Advisor: Jae-mook Lee}
	\item[] \hspace*{-5mm} \textit{Committee: Byung-won Woo, Woong-jin Kim, and specially Dae-jin Yi}
 	\item[]  \hspace*{-8mm} \underline{\smash{Concentration: Comparative Politics, Political Methodology, International Relations}}
\end{itemize}

\noindent {\bf B.A., \href{http://hufspol.hufs.ac.kr/}{Hankuk University of Foreign Studies}} \\
Department of Political Science and International Relations, February 2015
\begin{itemize} \itemsep -2pt 
	\item[] \hspace*{-8mm} Major: Political Science and International Relations
	\item[] \hspace*{-8mm} Minor: International Economics and Law
\end{itemize}

\section{PUBLICATION (\it{Peer-reviewed})} 
\begin{enumerate}[leftmargin=*]
	\item[7.] \textbf{Park, Sanghoon}, Chaehoon Lee, and Ilgi Kim. 2020. ``Infectious Disease Management and New Security Strategies: The Case of African Swine Fever in South Korea." \textit{The Journal of Peace Studies} 21(2): 143-174.
	\item[6.] \textbf{Park, Sanghoon}, and Jaeyoung Hur. 2020. ``\href{journal.kstudy.com/ISS_DownLoad.asp?a_code=0g000726.pdf&inst=3345&isDownLoad=1&code=YqldZWtoSqVtJTNEMnMoNSUmN/B Z xLJTNEVHJpZQ==}{Does North Korea Policies Reflect Public Opinion? The Public Awareness Survey Around the 4.27 Panmunjom Declaration}." \textit{Discourse 201} 23(2): 83-113.
	\item[5.] Lee, Jaehoon, and \textbf{Sagnhoon Park}. 2020. ``\href{https://m.nec.go.kr/portal/cmm/fms/FileDown.do?atchFileId=5d0ffae936edc42f3b4e864801f86a0f4096c44da03fede418b94067e8f9d0ea&fileSn=1&bbsId=&searchYear=}{Climate and Electoral Participation: The Effect of Particulate Matter on Election in South Korea}'' \textit{The study of Election} 1(12): 77-98.  
	\item[4.] \textbf{Park, Sanghoon}, Jaemook Lee, and Daejin Yi. 2017. \href{http://www.dbpia.co.kr/Journal/ArticleDetail/NODE07183479?TotalCount=1&Seq=1&q=%5B%EB%8F%85%EC%9E%AC%EA%B5%AD%EA%B0%80%EC%99%80%20%EC%9E%AC%EB%B6%84%EB%B0%B0%C2%A7coldb%C2%A72%C2%A751%C2%A73%5D&searchWord=%EC%A0%84%EC%B2%B4%3D%5E%24%EB%8F%85%EC%9E%AC%EA%B5%AD%EA%B0%80%EC%99%80%20%EC%9E%AC%EB%B6%84%EB%B0%B0%5E*&Multimedia=0&isIdentifyAuthor=0&Collection=0&SearchAll=%EB%8F%85%EC%9E%AC%EA%B5%AD%EA%B0%80%EC%99%80%20%EC%9E%AC%EB%B6%84%EB%B0%B0&isFullText=0&specificParam=0&SearchMethod=0&Sort=1&SortType=desc&Page=1&PageSize=20#}{``Dictatorships and Redistribution: Empirical Analysis of Redistribution by Dictatorships Sub-regime Type."} \textit{OUGHTOPIA} 32(1), 271-314.
	\item[3.] Oh, Sujin, \textbf{Sanghoon Park}, and Jaemook Lee. 2017. \href{http://www.dbpia.co.kr/Journal/ArticleDetail/NODE07131578?TotalCount=1&Seq=1&q=%5B%EC%9D%B4%EC%9E%AC%EB%AC%B5%20%EC%98%A4%EC%88%98%EC%A7%84%20%EB%B0%95%EC%83%81%ED%9B%88%20%EA%B3%84%EA%B8%89%ED%88%AC%ED%91%9C%C2%A7coldb%C2%A72%C2%A751%C2%A73%5D&searchWord=%EC%A0%84%EC%B2%B4%3D%5E%24%EC%9D%B4%EC%9E%AC%EB%AC%B5%20%EC%98%A4%EC%88%98%EC%A7%84%20%EB%B0%95%EC%83%81%ED%9B%88%20%EA%B3%84%EA%B8%89%ED%88%AC%ED%91%9C%5E*&Multimedia=0&isIdentifyAuthor=0&Collection=0&SearchAll=%EC%9D%B4%EC%9E%AC%EB%AC%B5%20%EC%98%A4%EC%88%98%EC%A7%84%20%EB%B0%95%EC%83%81%ED%9B%88%20%EA%B3%84%EA%B8%89%ED%88%AC%ED%91%9C&isFullText=0&specificParam=0&SearchMethod=0&Sort=1&SortType=desc&Page=1&PageSize=20#}{``Class Betrayal Voting and Political Knowledge in the 20th Korean General Election." \textit{Korean Political Science Review} 51(1), 153-180.}
	\item[2.] Park, Youngdeuk, \textbf{Sanghoon Park}. 2016. \href{http://kiss.kstudy.com/thesis/thesis-view.asp?key=3472800}{``Determinants of Voting Choice in Brexit Referendum: Skill Level and Job Competition in the Labor Market."} \textit{The Korean Journal of Area Studies} 34(3), 1-31.	
	\item[1.] \textbf{Park, Sanghoon}. 2015. \href{http://search.koreanstudies.net/thesis/thesis-view.asp?key=3438155}{``Welfare Expenditure and Economic Growth: The Sub-types of Welfare Expenditure of OECD countries."} \textit{Global Political Research} 9(2), 81-107.	
\end{enumerate}

\section{WORKS IN PROGRESS}
\begin{enumerate}[leftmargin=*]
	\item[6.] ``Heterogeneous Democratization: 	Elite Politics and Economic Sanctions."
	\item[5.] ``Why Do Authoritarian Regimes Provide the Welfare Programs?."
	\item[4.] ``Why Some Authoritarian Regimes Grow More than Other Authoritarian Regimes?."
	\item[3.] ``When Democratic Breakdown Happens? Inequality and Democratic Consolidation."
	\item[2.] ``The Welfare States without Labour in Asia: Power Resources Theory Revisited."
	\item[1.] ``Labour condition and the society: unstability and Infertility, the conditional effects of labour protection."
\end{enumerate}

\section{CONFERENCE PAPERS}
\begin{itemize}
	\item[2020] ``Why Do Authoritarian Regimes Provide Welfare?'' The Annual Conference for Midwest Political Science Association, Chicago, Illinois, United States.
	\item[2020] ``When Does Water Bring Conflicts?'' Carolinas Conflict Consortium, Charlotte, North Carolina, United States. \textit{Poster Presentation}
	\item[2020] ``Why Do Authoritarian Regimes Provide Welfare?'' The Annual Conference for Southern Political Science Association, Puerto Rico, United States.
	\item[2019] ``Why Do Authoritarian Regimes Provide Welfare?'' The World Congress for Korean Politics and Society, Seoul, Korea.
	\item[2018] ``Authoritarian welfare state and Inequality." The Summer Meeting of Korean Political Science Association, Busan, Korea.
	\item[2017] ``Political Regimes and Economic Growth: the autonomy and constraints of ruling institutions." The Winter Meeting of Korean Political Science Association, Seoul, Korea.
	\item[2017] ``Attitudes toward Security issues and Class Betrayal Voting." The Summer Meeting of the Korean Association of Party Studies, Busan, Korea (with Jaemook Lee and Youngdeuk Park).
	\item[2017] ``Asian Political Regimes and Economic Growth: the Non-linear Relationships and Indirect Path." The Closing Presentation of Institutes for Political Methodology, Taipei, Taiwan.
	\item[2017] ``Government Debt and Welfare expenditure: the heterogeneous effects of expenditures." The Summer Meeting of the Korean Association of International Studies, Jeonju, Korea (with Youngdeuk Park).
	\item[2017] ``Attitudes to North Korea and Vote Choice: The heterogeneous effect of political knowledge of North Korea." The World Congress for Korean Politics and Society, Seoul, Korea (with Gidong Kim).
	\item[2017] ``Aid and Redistribution: the distributional effects of aid in recipient countries." The World Congress for Korean Politics and Society, Seoul, Korea (with Suna Jeong).
	\item[2016] ``Class Betrayal Voting and Political Knowledge in the 20th Korean General Election." The Winter Meeting of the Korean Political Science Association, Seoul, Korea (with Sujin Oh).
	\item[2016] ``The North Korea as Dictatorship: How It Redistributes for What." The Annual Meeting of The Korean Association of Peace Studies, Jeju, Korea.
	\item[2016] ``Dictatorships and Redistribution: Empirical Analysis of Redistribution by Dictatorship Sub-regime Type." The Summer Meeting of the Korean Political Science Association, Seoul, Korea.
\end{itemize}

\section{RESEARCH INTERESTS}
Comparative Politics: Authoritarian regimes; Democratization; Regime breakdown; Comparative institutions; Political economics of inequality and redistribution

\section{RESEARCH EXPERIENCE} 
 \begin{itemize}
 	\item[2016] Research Assistant for Jaemook Lee, Department of Political Science, Hankuk University of Foreign Studies.: Sponsored from People's Party, Korea. ``An Analysis on Voter’s Perception and Preference upon People’s Party."
 	\item[2015] Research Assistant for Ilgi Kim, Institute for National Security Strategy.: Sponsored from Ministry of Unification, Korea. ``The Verification of the Nuclear Disarmament."
 	\item[2015] Research Assistant for Sanghwan Lee, Department of Political Science, Hankuk University of Foreign Studies.: Sponsored from National Research Foundation of Korea, Korea. ``Health Cooperation and Conflict among G20 Countries: Focusing on the Epidemic Cases of Global Society in the 21th Century"
 \end{itemize}
 
\section{HONORS \& REWARDS} 
\begin{itemize}[wide = 0pt] \itemsep -2pt 
	\item[2018-2023] \textbf{University of South Carolina, Department of Political Science, Columbia, SC}
	\begin{itemize} \itemsep -2pt 
		\item[$\circ$] ACAF 4.00 Graduate Assistantships
	\end{itemize} \itemsep -2pt 
	\item[2020] \textbf{Empirical Implications of Theoretical Models Institute}
	\begin{itemize} \itemsep -2pt 
		\item[$\circ$] \href{https://52.2.147.143/icpsrweb/content/sumprog/scholarships/winners-2020.html}{EITM Certification Scholarships: To attend both sessions at the ICPSR Summer Program} (\$4,000)
	\end{itemize} 
	\item[2020] \textbf{Department of Political Science, University of South Carolina}
	\begin{itemize} \itemsep -2pt 
		\item[$\circ$] Outstanding Graduate Student Awards
	\end{itemize} 
	\item[2020] \textbf{Department of Political Science, University of South Carolina}
	\begin{itemize} \itemsep -2pt 
		\item[$\circ$] The Second Annual Conference Funding Competition: Joint award (\$500)
	\end{itemize} 
	\item[2019] \textbf{The Institute for National Security Strategy, INSS}
	\begin{itemize} \itemsep -2pt 
		\item[$\circ$] The 1st New Security Papers Contest: Second Prize (\$2,000)
		\item[$\circ$] Title: Infectious Disease Management and New Security Strategies: The Case of African Swine Fever in South Korea
	\end{itemize}
	\item[2015-2017] \textbf{Hankuk University of Foreign Studies}
	\begin{itemize} \itemsep -2pt 
		\item[$\circ$] Merit based, Graduate Full Scholarship for HUFSAN
	\end{itemize}
\end{itemize}

\section{PROFESSIONAL AFFILIATION} 
 \begin{itemize}[wide = 0pt] \itemsep -2pt 
 	\item[ ] Member of Midwest Political Science Association
 	\item[ ] Member of Southern Political Science Association
\end{itemize}

\section{ADDITIONAL TRAININGS} 
\begin{itemize}[wide = 0pt] \itemsep -2pt 
	\item[2020] Summer Program in Quantitative Methods of Social Research, University of Michigan (U.S.)
	\begin{itemize}
		\item[$\circ$] \textit{First Session: June 22-July 17, 2020}
		\begin{enumerate}
			\item Bayesian Modeling for the Social Sciences I: Introduction and Application
			\item Maximum Likelihood Estimation I: Generalized Linear Models
			\item Introduction to Python (July 6-17)
		\end{enumerate}
		\item[$\circ$] \textit{Second Session, July 20-August 14, 2020}
		\begin{enumerate}
			\item Game Theory
			\item Bayesian Modeling for the Social Sciences II: Advanced Topics
			\item Causal Inference for the Social Sciences
		\end{enumerate}
	\end{itemize}
	\item[2018] Social Science Data Innovation Center, Yonsei University (Korea)
	\begin{itemize}
	\item[$\circ$] Introduction to R
	\end{itemize}
	\item[2017] Institute for Political Methodology (Taiwan): Cross-level Analysis
	Statistics
	\begin{itemize} \itemsep -2pt 
		\item[$\circ$] Hierarchical Age-Period-Cohort Analysis
		\item[$\circ$] Multi-level Analysis
		\item[$\circ$] Multi-level Synthesis: A Spatial Microsimulation Approach
	\end{itemize}
	\item[2017] Hankuk University of Foreign Studies (Korea)
	\begin{itemize} \itemsep -2pt 
		\item[$\circ$] Data Handling with PYTHON 
	\end{itemize}		
	\item[2017] Social Science Data Innovation Center, Yonsei University (Korea)
	\begin{itemize}
		\item[$\circ$] Text Analysis and Network Analysis with PYTHON 
	\end{itemize}
\end{itemize}

\section{PROFESSIONAL SKILLS}
\begin{itemize}[wide=0pt]
	\item[\textit{\bf Languages}] \textbf{Korean}: native. \textbf{Japanese}: native. \textbf{English}: advanced.
	\item[\textit{\bf Programming}] R, STATA, Python, \LaTeX, Markdown
\end{itemize}
\mbox{}
\vfill
\centering \textit{Last updated: \today}

\end{resume}
\end{document}











