\documentclass[margin,line]{res}
\usepackage{enumitem}
\usepackage{fontawesome}
\usepackage{hyperref}
\usepackage{xcolor}
\hypersetup{
	colorlinks,
	linkcolor={red!50!black},
	citecolor={red!50!black},
	urlcolor={blue!50!black}
}

\pagestyle{plain}
\setcounter{page}{1}

\oddsidemargin -.5in
\evensidemargin -.5in
\textwidth=6.0in
\itemsep=0in
\parsep=0in
% if using pdflatex:
%\setlength{\pdfpagewidth}{\paperwidth}
%\setlength{\pdfpageheight}{\paperheight} 

\newenvironment{list1}{
  \begin{list}{\ding{113}}{%
      \setlength{\itemsep}{0in}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{0in} \setlength{\partopsep}{0in} 
      \setlength{\leftmargin}{0.17in}}}{\end{list}}
\newenvironment{list2}{
  \begin{list}{$\bullet$}{%
      \setlength{\itemsep}{0in}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{0in} \setlength{\partopsep}{0in} 
      \setlength{\leftmargin}{0.2in}}}{\end{list}}

\usepackage{setspace}
\renewcommand{\baselinestretch}{1.0} 


\begin{document}

\name{\huge Sanghoon Park \vspace*{.1in}}

\begin{resume}
\section{\sc Contact Information}
\vspace{.05in}
\begin{tabular}{@{}p{2in}p{4in}}
\faBuildingO\:\#305 Gambrell Hall & {\faPhoneSquare}  +1 (803) 626-2252 \\  
817 Henderson Street & {\faEnvelope}  \href{sp23@email.sc.edu}{\ttfamily sp23@email.sc.edu} \\

Columbia, SC 29208 & {\faChain} \href{sanghoon-park.com}{\ttfamily sanghoon-park.com}\\       
& {\faGithub} \href{https://github.com/pherephobia}{\ttfamily github.com/pherephobia}\\     
%& {ORCID ID}: \href{https://orcid.org/0000-0001-5365-0013}{0000-0001-5365-0013}

\end{tabular}

\section{\sc Education}
{\bf University of South Carolina}, Columbia, SC, US\\
Ph.D. Candidate in Political Science, expected 2023\\
\vspace*{-4mm}
%\hspace*{-8mm} Dissertation: {\it My Dissertation title}\\ 
%\hspace*{3mm} Concentration: {\it Comparative Politics, International Relations}\\
\begin{itemize} \itemsep -1mm 
	\item[]  \hspace*{-6mm} Fields for comprehensive exams:\\{\it Comparative Politics} (Major, passed with distinction), {\it International Relations} (Minor)
\end{itemize}
%\hspace*{-8mm} Advisors: Drs. Wilson C.  (Biology) \& James G. McDaniel (Mechanical Engineering)	
\vspace*{-1.5mm}

{\bf Hankuk University of Foreign Studies}, Seoul, ROK

\vspace*{-4mm}
M.A. in Political Science and International Relations, February 2017\\
\vspace*{-4mm}
\begin{itemize} \itemsep -1mm 
	\item[]  \hspace*{-6mm} Thesis: {\it Dictatorships and Redistribution: Empirical Analysis of Redistribution by Dictatorship Sub-regime Types}
	\item[]  \hspace*{-6mm} Advisor: Dr. Jaemook Lee (Political Science), and specially Daejin Yi (Political Science)
\end{itemize}
\vspace*{-3mm}
B.A. in Political Science and International Relations, February 2015\\
\vspace*{-4mm}
\begin{itemize} \itemsep -1mm
	\item[]  \hspace*{-6mm} Major: Political Science and International Relations
	\item[]  \hspace*{-6mm} Minor: International Economics and Law
\end{itemize}

\section{\sc Research Interests}
{\bf Comparative Politics} Authoritarian regimes, Democratization, Regime breakdown, Comparative institutions, Political economics of inequality and redistribution

\vspace{-.3cm}
{\bf International Relations} Democratic diffusion, Economic sanctions, Foreign aids

\section{\sc Peer-Reviewed Articles}

\begin{enumerate}[leftmargin=*]
\item[9.] \textbf{Park, Sanghoon}. 2022. ``\href{http://www.partystudies.or.kr/contents/bbs/bbs_list.html?bbs_cls_cd=004003}{Effect of reasons for re-election on voting participation and outcomes: An empirical examination of re/by-elections for the Korean National Assembly after democratization.}"  \textit{Korean Party Studies Review} 21(3): 41-80. 
\item[8.] Kang, Jiyoon, \textbf{Sanghoon Park}, and Sun Gue Yang. 2022. ``\href{http://basicdata.kr/board/read/journals/146/}{Leadership in Communication:
How Leadership and Communication Affect Public Service Motivation (PSM)}." \textit{Journal of Research Methodology} 7(1): 23-60.
\item[7.] \textbf{Park, Sanghoon}, Chaehoon Lee, and Ilgi Kim. 2020. ``\href{https://www.earticle.net/Journal/Issues/511/28448}{Infectious Disease Management and New Security Strategies: The Case of African Swine Fever in South Korea}." \textit{The Journal of Peace Studies} 21(2): 143-174.
\item[6.] \textbf{Park, Sanghoon}, and Jaeyoung Hur. 2020. ``\href{http://www.discourse201.org/html/sub05_01.asp}{Does North Korea Policies Reflect Public Opinion? The Public Awareness Survey Around the 4.27 Panmunjom Declaration}." \textit{Discourse 201} 23(2): 83-113.
\item[5.] Lee, Jaehoon, and \textbf{Sagnhoon Park}. 2020. ``\href{https://m.nec.go.kr/portal/cmm/fms/FileDown.do?atchFileId=5d0ffae936edc42f3b4e864801f86a0f4096c44da03fede418b94067e8f9d0ea&fileSn=1&bbsId=&searchYear=}{Climate and Electoral Participation: The Effect of Particulate Matter on Election in South Korea}'' \textit{The Study of Election} 12(1): 77-98.  
\item[4.] \textbf{Park, Sanghoon}, Jaemook Lee, and Daejin Yi. 2017. \href{http://www.dbpia.co.kr/Journal/ArticleDetail/NODE07183479?TotalCount=1&Seq=1&q=%5B%EB%8F%85%EC%9E%AC%EA%B5%AD%EA%B0%80%EC%99%80%20%EC%9E%AC%EB%B6%84%EB%B0%B0%C2%A7coldb%C2%A72%C2%A751%C2%A73%5D&searchWord=%EC%A0%84%EC%B2%B4%3D%5E%24%EB%8F%85%EC%9E%AC%EA%B5%AD%EA%B0%80%EC%99%80%20%EC%9E%AC%EB%B6%84%EB%B0%B0%5E*&Multimedia=0&isIdentifyAuthor=0&Collection=0&SearchAll=%EB%8F%85%EC%9E%AC%EA%B5%AD%EA%B0%80%EC%99%80%20%EC%9E%AC%EB%B6%84%EB%B0%B0&isFullText=0&specificParam=0&SearchMethod=0&Sort=1&SortType=desc&Page=1&PageSize=20#}{``Dictatorships and Redistribution: Empirical Analysis of Redistribution by Dictatorships Sub-regime Type."} \textit{OUGHTOPIA} 32(1), 271-314.
\item[3.] Oh, Sujin, \textbf{Sanghoon Park}, and Jaemook Lee. 2017. \href{http://www.dbpia.co.kr/Journal/ArticleDetail/NODE07131578?TotalCount=1&Seq=1&q=%5B%EC%9D%B4%EC%9E%AC%EB%AC%B5%20%EC%98%A4%EC%88%98%EC%A7%84%20%EB%B0%95%EC%83%81%ED%9B%88%20%EA%B3%84%EA%B8%89%ED%88%AC%ED%91%9C%C2%A7coldb%C2%A72%C2%A751%C2%A73%5D&searchWord=%EC%A0%84%EC%B2%B4%3D%5E%24%EC%9D%B4%EC%9E%AC%EB%AC%B5%20%EC%98%A4%EC%88%98%EC%A7%84%20%EB%B0%95%EC%83%81%ED%9B%88%20%EA%B3%84%EA%B8%89%ED%88%AC%ED%91%9C%5E*&Multimedia=0&isIdentifyAuthor=0&Collection=0&SearchAll=%EC%9D%B4%EC%9E%AC%EB%AC%B5%20%EC%98%A4%EC%88%98%EC%A7%84%20%EB%B0%95%EC%83%81%ED%9B%88%20%EA%B3%84%EA%B8%89%ED%88%AC%ED%91%9C&isFullText=0&specificParam=0&SearchMethod=0&Sort=1&SortType=desc&Page=1&PageSize=20#}{``Class Betrayal Voting and Political Knowledge in the 20th Korean General Election." \textit{Korean Political Science Review} 51(1), 153-180.}
\item[2.] Park, Youngdeuk, \textbf{Sanghoon Park}. 2016. \href{http://kiss.kstudy.com/thesis/thesis-view.asp?key=3472800}{``Determinants of Voting Choice in Brexit Referendum: Skill Level and Job Competition in the Labor Market."} \textit{The Korean Journal of Area Studies} 34(3), 1-31.	
\item[1.] \textbf{Park, Sanghoon}. 2015. \href{http://search.koreanstudies.net/thesis/thesis-view.asp?key=3438155}{``Welfare Expenditure and Economic Growth: The Sub-types of Welfare Expenditure of OECD countries."} \textit{Global Political Research} 9(2), 81-107.	
\end{enumerate}

\section{\sc Other Publications}
\begin{enumerate}[leftmargin=*]
  \item[2.] Wilson, Matthew and \textbf{Sanghoon Park}. "Empirical Indicators of Democracy and Authoritarianism." In {\it Oxford Bibliographies in Political Science}. Ed. Sandy Maised. New York: Oxford University Press, {\it forthcoming}.
	\item[1.] \textbf{Park, Sanghoon} and Jaeyoung Hur. 2021. "What do we know and do not know?: Attitudes toward North Korea and unification." In {\it Issues and Perspectives in Korean Peace Process.} Hankuk University of Foreign Studies Knowledge Contents \& Press.
\end{enumerate}

\section{\sc Under review}
\begin{enumerate}[leftmargin=*]
\item[3.] Wilson, Charles Matthew, Christopher Howell, Kelsey Martin-Morales, and \textbf{Sanghoon Park}. 2022. ``Concept Mapping and Reading Comprehension."
\item[2.] Park, Chun-Young and \textbf{Sanghoon Park}. 2022. ``You Scratch My Back, and I Scratch Yours: An Explanation of Dyadic Politics of Naming and Shaming."
\item[1.] Hur, Jaeyoung, Hyun-Hee Heo, \textbf{Sanghoon Park}, Deok-Hyun Jang, Jin-Yong Lee, Jin-Yong, and Won-Mo Jang. 2022. ``Risk Perceptions, Ideology, and Voting Intentions During the COVID-19 Pandemic: A Cross-sectional Study in South Korea."
% \item[1.] Jaeyoung, Hur, \textbf{Sanghoon Park}, Hannah Kim, and Taehee Whang. 2021. ``Social Capital and the Success of Economic Sanction."
\end{enumerate}

%\section{\sc Manuscripts in Preparation}

%\begin{enumerate}[leftmargin=*]
%\item[1.] Jaeyoung, Hur, \textbf{Sanghoon Park}, Hannah Kim, and Taehee Whang. 2021. ``Social Capital and the Success of Economic Sanciton." ({\it in preparation} for submission to {\it Journal of Peace Research}.)

\section{\sc Work\\in progress}

\begin{enumerate}[leftmargin=*]
	\item[4.] ``Expanding China's Influence in the International Human Rights Regime: Analysis of UN UPR Recommendations." (with Hyunkyu Kim)
	\item[3.] ``Party Institutionalization and Civil Conflict" (with Dr. Matthew C. Wilson)
	\item[2.] ``Digital Technology and the Choice to Repress or Co-opt" (with Emily Harmon and\\ Kuanwu Chen)
	%\item[2.] ``You Scratch My Back and I Scratch Yours: An Explanation of Dyadic Politics of Naming and Shaming"
	% \item[3.] ``Heterogeneous Democratization: 	Elite Politics and Economic Sanctions."
	\item[1.] ``Why Do Authoritarian Regimes Provide the Welfare Programs?"
%	\item[4.] ``Why Some Authoritarian Regimes Grow More than Other Authoritarian Regimes?."
%	\item[3.] ``When Democratic Breakdown Happens? Inequality and Democratic Consolidation."
	% \item[1.] ``The Welfare States without Labour in Asia: Power Resources Theory Revisited."
%	\item[1.] ``Labour condition and the society: unstability and Infertility, the conditional effects of labour protection."
\end{enumerate}

\section{\sc Honors, Awards, and Grants} 

\begin{itemize}[wide = 0pt] \itemsep 1.5mm
	\item[2018-2023] \textbf{University of South Carolina, Department of Political Science, SC, US}
	\begin{itemize} 
		\item[$\circ$] ACAF 4.00 Graduate Assistantships
	\end{itemize} 
	\item[2022] \textbf{Empirical Implications of Theoretical Models Institute}
	\begin{itemize}
		\item[$\circ$] \href{https://eitminstitute.org/institute/2022/}{2022 EITM Summer Institute} (\$750)
	\end{itemize} 
	\item[2020] \textbf{Empirical Implications of Theoretical Models Institute}
	\begin{itemize}
		\item[$\circ$] \href{https://52.2.147.143/icpsrweb/content/sumprog/scholarships/winners-2020.html}{EITM Certification Scholarships: Both sessions at the ICPSR Summer Program} (\$4,000)
	\end{itemize} 
	\item[2020] \textbf{Department of Political Science, University of South Carolina, SC, US}
	\begin{itemize}
		\item[$\circ$] Outstanding Graduate Student Awards
	\end{itemize} 
	\item[2020] \textbf{Department of Political Science, University of South Carolina, SC, US}
	\begin{itemize}
		\item[$\circ$] The Second Annual Conference Funding Competition: Joint award (\$500)
	\end{itemize} 
	\item[2019] \textbf{The Institute for National Security Strategy (INSS), Seoul, ROK}
	\begin{itemize}\itemsep -1mm 
		\item[$\circ$] The 1st New Security Papers Contest: Second Prize (\$2,000)
		\item[$\circ$] Title: Infectious Disease Management and New Security Strategies: The Case of African Swine Fever in South Korea
	\end{itemize}
	\item[2015-2017] \textbf{Hankuk University of Foreign Studies, Seoul, ROK}
	\begin{itemize} 
		\item[$\circ$] Merit based, Graduate Full Scholarship for HUFSAN
	\end{itemize}
\end{itemize}

\section{\sc Conference Presentations}

Kim, Hyun-kyu and {\bf Sanghoon Park}. {2022.} {``Chinese Foreign Policy and the Evolution of Human Rights Discourse.''} {\it The Summer Meeting of the Korean Association of International Studies,} Seoul, ROK.

\vspace{-.25cm}
{\bf Park, Sanghoon} and Chunyoung Park. {2022.} {``You Scratch My Back and I Scratch Yours: An Explanation of Dyadic Politics of Naming and Shaming.''} {\it The Annual Conference for Midwest Political Science Association,} Chicago, IL, US.

\vspace{-.25cm}
Wilson, Matthew Charles, Chris Howell, Kelsey Morgan Martin Morales, and {\bf Sanghoon Park}. {2022.} {``Concept Mapping and Reading Comprehension.''} {\it The Annual Conference for Midwest Political Science Association,} Chicago, IL, US.

\vspace{-.25cm}
Jiyoon Kang and {\bf Park, Sanghoon}. {2022.} {``Willing to be a protester: Violence, solidarity, and durability of protests.''} {\it the 63rd ISA Annual Convention,} Nashville, TN, US.

\vspace{-.25cm}
{\bf Park, Sanghoon}, Emily Harmon, and Kuan-Wu Chen. {2022.} {``Digital Technology and the Choice to Repress or Co-opt.''} {\it the 63rd ISA Annual Convention,} Nashville, TN, US.

\vspace{-.25cm}
{\bf Park, Sanghoon}. {2022.} {``Social Capital and the Success of Economic Sanction."} {\it third annual Carolinas Conflict Consortium,} Columbia, SC, US.

\vspace{-.25cm}
{\bf Park, Sanghoon} and Chunyoung Park. {2021.} {``You Scratch My Back and I Scratch Yours: An Explanation of Dyadic Politics of Naming and Shaming.''} {\it ISA-South Annual Meeting 2021,} Atlanta, GA, US.

\vspace{-.25cm}
{\bf Park, Sanghoon}. {2021.} {``Heterogeneous Democratization: Economic Sanctions and Elite Politics''} {\it The Annual Conference for Midwest Political Science Association,} Virtual conference.

\vspace{-.25cm}
{\bf Park, Sanghoon}. {2020.} {``Why Do Authoritarian Regimes Provide Welfare Programs?''} {\it The Annual Conference for Midwest Political Science Association,} Chicago, IL, US.

\vspace{-.25cm}
{\bf Park, Sanghoon}. {2020.} \href{https://www.dropbox.com/s/7xr90ielm1vh1sd/poster.pdf?dl=0}{\tt Poster PDF.} {``When Does Water Bring Conflicts?''} {\it second annual Carolinas Conflict Consortium,} Charlotte, NC, US.

\vspace{-.25cm}
{\bf Park, Sanghoon}. {2020.} {``Why Do Authoritarian Regimes Provide Welfare?''} {\it The Annual Conference for Southern Political Science Association,} San Juan, PR, US.

\vspace{-.25cm}
{\bf Park, Sanghoon}. {2019.} {``Why Do Authoritarian Regimes Provide Welfare?''} {\it The World Congress for Korean Politics and Society,} Seoul, ROK.

\vspace{-.25cm}
{\bf Park, Sanghoon}. {2018.} {``Authoritarian Welfare State and Inequality''} {\it The Summer Meeting of Korean Political Science Association,} Busan, ROK.

\vspace{-.25cm}
{\bf Park, Sanghoon}. {2017.} {``Political Regimes and Economic Growth: The Autonomy and Constraints of Ruling Institutions''} {\it The Winter Meeting of Korean Political Science Association,} Seoul, ROK.

\vspace{-.25cm}
{\bf Park, Sanghoon}, Jaemook Lee, and Youngdeuk Park. {2017.} {``Attitudes toward Security issues and Class Betrayal Voting.''} {\it The Summer Meeting of the Korean Association of Party Studies,} Busan, ROK.

\vspace{-.25cm}
{\bf Park, Sanghoon}. {2017.} {``Asian Political Regimes and Economic Growth: the Non-linear Relationships and Indirect Path.''} {\it The Closing Presentation of Institutes for Political Methodology,} Taipei, TW.

\vspace{-.25cm}
{\bf Park, Sanghoon} and Youngdeuk Park. {2017.} {``Government Debt and Welfare expenditure: the heterogeneous effects of expenditures.''} {\it The Summer Meeting of the Korean Association of International Studies,} Jeonju, ROK.

\vspace{-.25cm}
{\bf Park, Sanghoon} and Gidong Kim. {2017.} {``Attitudes to North Korea and Vote Choice: The heterogeneous effect of political knowledge of North Korea.''} {\it The World Congress for Korean Politics and Society,} Seoul, ROK.

\vspace{-.25cm}
{\bf Park, Sanghoon} and Suna Jeong. {2017.} {``Aid and Redistribution: the distributional effects of aid in recipient countries.''} {\it The World Congress for Korean Politics and Society,} Seoul, ROK.

\vspace{-.25cm}
{\bf Park, Sanghoon} and Sujin Oh. {2016.} {``Class Betrayal Voting and Political Knowledge in the 20th Korean General Election.''} {\it The Winter Meeting of the Korean Political Science Association,} Seoul, ROK.

\vspace{-.25cm}
{\bf Park, Sanghoon}. {2016.} {``The North Korea as Dictatorship: How It Redistributes for What.''} {\it The Annual Meeting of The Korean Association of Peace Studies,} Jeju, ROK.

\vspace{-.25cm}
{\bf Park, Sanghoon}. {2016.} {``Dictatorships and Redistribution: Empirical Analysis of Redistribution by Dictatorship Sub-regime Type.''} {\it The Summer Meeting of the Korean Political Science Association,} Seoul, ROK.

\section{\sc Research Experience}
%{\bf Dissertation Research},  University of South Carolina, start date - end date

%\vspace{-.43cm}
%{Advisors: Professors Wilson C. Matthew (Political Science). Project: title. }

%\vspace{-.1cm}

{\bf Graduate Research Assistant}, the College of Arts and Sciences Incubator for Teaching Innovation, University of South Carolina, 2020-21.

\vspace{-.43cm}

The College of Arts and Sciences Innovative Teaching Associate Program 

\vspace{-.43cm}

Principal investigator:  Professor Wilson C. Matthew \small{(Political Science, University of South Carolina)}
\vspace{-.43cm}
\begin{itemize}
	\item[] Fall 2021: Project leader
	\item[] Spring 2020: Project participant
	\item[] Fall 2020: Project participant
\end{itemize}

\vspace{-.1cm}
{\bf Research Assistant}, National Assembly Research Service, ROK, 2021.

\vspace{-.43cm}

A Study on Activation of Democratic Political Participation in the Post-COVID-19 Era

\vspace{-.43cm}

Principal investigator: Professor Jaemook Lee \small{(Political Science, Hankuk University of Foreign Studies)}

\vspace{-.43cm}

Co-investigator: Dr. Soohyun Jung \small{(Korea Institute for Future Politics, Myongji University)}\\
Co-investigator: Dr. Youngdeuk Park \small{(Political Science, Chungnam National University)}

\vspace{-.1cm}

{\bf Principal investigator}, Korea Democracy Foundation, 2020.

\vspace{-.43cm}

The Barriers COVID-19 Re-established: What Makes Democracy Sick?

\vspace{-.43cm}
Co-Principal investigator: M.A. Chaehoon Lee \small{(Korean Standards Association)}

\vspace{-.1cm}
{\bf Research Assistant}, People's Party, ROK, 2016.

\vspace{-.43cm}

An Analysis on Voter’s Perception and Preference upon People’s Party.

\vspace{-.43cm}

Principal investigator: Professor Jaemook Lee \small{(Political Science, Hankuk University of Foreign Studies)}

\vspace{-.1cm}
{\bf Research Assistant}, Ministry of Unification, ROK, 2015.

\vspace{-.43cm}

The Verification of the Nuclear Disarmament.

\vspace{-.43cm}
Principal investigator: Dr. Ilgi Kim \small{(The Institute for National Security Strategy)}

\vspace{-.1cm}
{\bf Research Assistant}, National Research Foundation of Korea, 2015.

\vspace{-.43cm}
Health Cooperation and Conflict among G20 Countries: Focusing on the Epidemic Cases of Global Society in the 21th Century

\vspace{-.43cm}
Principal investigator: Professor Sanghwan Lee \small{(Political Science, Hankuk University of Foreign Studies)}

\section{\sc Teaching Experience} 

{\bf Instructor}, University of South Carolina, Columbia
\vspace{-.55cm}
\begin{itemize} \itemsep -0.3mm 
	\item[2022] International Relations (U)
	\item[2021] Comparative Politics (U)
\end{itemize}
\vspace{-.3cm}
{\bf Teaching Assistant}, University of South Carolina, Columbia
\vspace{-.55cm}
\begin{itemize} \itemsep -0.3mm 
	\item[2022] American National Government (U)
	\item[2021] Introduction to Global Politics (U)
	\item[2020] Introduction to Global Politics (U)
	\item[2020] Genocide: A Comparative Perspective (U)
	\item[2019] International Relations (U)
	\item[2019] Democratic Theory (U)
	\item[2018] Comparative Politics (U)
\end{itemize}
\vspace{-.3cm}
{\bf Teaching Assistant}, Hankuk Univsersity of Foreign Studies, Seoul, ROK
\vspace{-.55cm}
\begin{itemize} \itemsep -0.3mm 
	\item[2016] Research Methodology in Political Science
	\item[2015] Civil Society
\end{itemize}

\section{\sc Teaching Interests}

{\bf Comparative Politics} Introduction to Comparative Politics, Democracy and Dictatorship, Comparative institutions
\vspace{-.25cm}

{\bf International Relations} Introduction to International Relations
\vspace{-.25cm}

{\bf Political Methodology} Introduction to Statistical Methods for Political Science
\vspace{-.25cm}

\section{\sc Professional Affiliation}

{\bf Graduate Student Member}, {\it American Political Science Association}, 2021 - Present
\vspace{-.25cm}

{\bf Graduate Student Member}, {\it Midwest Political Science Association}, 2019 - Present
\vspace{-.25cm}

{\bf Graduate Student Member}, {\it Southern Political Science Association}, 2019 - Present
\vspace{-.25cm}

{\bf Graduate Student Member}, {\it International Studies Association}, 2021 - Present

\section{\sc Professional Service Activities}
\vspace{-.3cm}
\begin{itemize} \itemsep -0.3mm 
	\item[] 2018-Present International Relations and Comparative Politics Brown bag Meeting.
	\begin{itemize}
		\item[] 2018-Present Discussant
		\item[] 2021 Fall Chair
	\end{itemize}
	\item[] 2022 Chair, The Annual Conference for Midwest Political Science Association.
\end{itemize}

\section{\sc Extra Curriculum \& Skills} 

{\bf EITM Summer Institute}, University of California, Berkeley, CA, 2022.
\vspace{-.4cm}
\begin{itemize} \itemsep -1mm 
	\item[$\circ$] \textit{Training for a research strategy of EITM: June 27- Jul 15, 2021}
	\begin{itemize} \itemsep -1mm 
		\item Causal inference and theoretical models 
		\item Practicum on building theoretical models
		\item Theory evaluation in experimental, observational, and qualitative research 
		\item The role of theory and identification in generalized causal inference   
		\item Theory building and evaluation in comparative politics, international relations, political behavior, and political institutions 
	\end{itemize}
\end{itemize}
\vspace{-.25cm}
{\bf ICPSR Summer Program}, University of Michigan, MI, US, 2021.
\vspace{-.4cm}
\begin{itemize} \itemsep -1mm 
	\item[$\circ$] \textit{Short Workshop: May 17-28, 2021}
	\begin{itemize} \itemsep -1mm 
		\item Network Analysis: Statistical Approach
	\end{itemize}
\end{itemize}
\vspace{-.25cm}
{\bf ICPSR Summer Program}, University of Michigan, MI, US, 2020.
\vspace{-.4cm}
\begin{itemize} \itemsep -1mm 
	\item[$\circ$] \textit{First Session: June 22-July 17, 2020}
	\begin{enumerate} \itemsep -1mm 
		\item Bayesian Modeling for the Social Sciences I: Introduction and Application
		\item Maximum Likelihood Estimation I: Generalized Linear Models
		\item Introduction to Python (July 6-17)
	\end{enumerate}
	\item[$\circ$] \textit{Second Session, July 20-August 14, 2020}
	\begin{enumerate} \itemsep -1mm 
		\item Game Theory
		\item Bayesian Modeling for the Social Sciences II: Advanced Topics
		\item Causal Inference for the Social Sciences
	\end{enumerate}
\end{itemize}

\vspace{-.1cm}

{\bf Introduction to R}, Social Science Data Innovation Center, Yonsei University, ROK, 2018.

\vspace{-.1cm}

{\bf IPM2017: Cross-level Analysis}, Institute for Political Methodology in Taiwan, TW, 2017.
\vspace{-.4cm}
\begin{itemize} \itemsep -1mm 
	\item[$\circ$] Hierarchical Age-Period-Cohort Analysis
	\item[$\circ$] Multi-level Analysis
	\item[$\circ$] Multi-level Synthesis: A Spatial Microsimulation Approach
\end{itemize}

{\bf Data Handling with PYTHON}, Hankuk University of Foreign Studies, ROK, 2017.

\vspace{-.1cm}

{\bf Text Analysis and Network Analysis with PYTHON}, Social Science Data Innovation Center, Yonsei University, ROK, 2017.
\vspace{-.1cm}

{\bf Computing Skills}: R, STATA, Python, \LaTeX, Markdown, Git \& Github

\vspace*{-3mm}
{\bf Languages}:  Korean (fluent), Japanese (fluent), English (highly proficient)
%{\bf Certifications}: 
%\vspace*{-3mm}


\mbox{}
\vfill
\centering \textit{Last updated: \today}


\end{resume}

\end{document}
$\]
\end{document}